Mental Wellbeing Pathways

### 2023-03-01 minos/validation/mwb_pathways.Rmd
Added hh_income and SF12 to mwb_pathways notebook

>>>>

## SF 12

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12 = mean(SF_12))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
sf12.2018 <- sf12 %>% filter(time == 2018)
sf12.2020 <- sf12 %>% filter(time == 2020)
sf12.2030 <- sf12 %>% filter(time == 2030)

sf12.joined <- rbind(sf12.2018, sf12.2020, sf12.2030)
sf12.joined$time <- as.factor(sf12.joined$time)

ggplot(data = sf12.joined, mapping = aes(x = SF_12, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

TODO: Why are we getting the same exact values from 2020 - 2030?

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12))
sprintf("Max: %f", max(sf12.2018$SF_12))
sprintf("Mean: %f", mean(sf12.2018$SF_12))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12))
sprintf("Max: %f", max(sf12.2020$SF_12))
sprintf("Mean: %f", mean(sf12.2020$SF_12))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12))
sprintf("Max: %f", max(sf12.2030$SF_12))
sprintf("Mean: %f", mean(sf12.2030$SF_12))
```

## hh_income

TODO: PLOT THE RAW DATA!!!

```{r}
income <- data %>% 
  select(pidp, time, hh_income)

# calculate and plot mean over time
income.byyr <- data %>% group_by(time) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.byyr, mapping = aes(x = time, y = hh_income)) +
  geom_line()
```

Again lets try overlaid histograms to see distributions over time.

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
income.2018 <- income %>% filter(time == 2018)
income.2020 <- income %>% filter(time == 2020)
income.2030 <- income %>% filter(time == 2030)

income.joined <- rbind(income.2018, income.2020, income.2030)

income.joined$time <- as.factor(income.joined$time)
income.joined$hh_income <- as.numeric(income.joined$hh_income)

ggplot(data = income.joined, mapping = aes(x = hh_income, group = time, fill = time, color = time)) +
  geom_histogram(bins = 50, position='dodge')
```

Check out the min/max for each time point, looks like it spreads out massively.
```{r}
print("2018:")
sprintf("Min: %f", min(income.2018$hh_income))
sprintf("Max: %f", max(income.2018$hh_income))
sprintf("Mean: %f", mean(income.2018$hh_income))
print("2020:")
sprintf("Min: %f", min(income.2020$hh_income))
sprintf("Max: %f", max(income.2020$hh_income))
sprintf("Mean: %f", mean(income.2020$hh_income))
print("2030:")
sprintf("Min: %f", min(income.2030$hh_income))
sprintf("Max: %f", max(income.2030$hh_income))
sprintf("Mean: %f", mean(income.2030$hh_income))
```
